Automated Formal Synthesis of Digital Controllers for State-Space Physical Plants

### 2017-01-16 cav2017/cav2017.tex
cav

%-------------------------------
\subsection{Digital implementation of feedback controller}
\label{ssec:statefeedbackcontrol}
%-------------------------------

%-------------------------------
\subsection{Quantization error in digital controllers of Cyber-Physical Systems}
\label{ssec:quantizationerror}
%-------------------------------

@@

>>>>

%-------------------------------
\subsection{Digital implementation of feedback controller}
\label{ssec:quantizationerror}
%-------------------------------

\todo{HERE add a figure similar to Fig. \label{fig:observersystem} to explain digital features of controller.}

@@

\todo{The safety specification is defined over the state space, not the output. Further, please distinguish the spec from the input constraints. }
